---
title: "Thymio AR Optique"
output:
  html_notebook: default
  html_document: default
---

This sheet presents results of the experiment conducted with two classrooms and aiming to show the effect in terms of learning outcome of the use of augmented reality in a task where learners had to understand basic optic principles related to IR sensors of Thymio.

The source code of this analysis is online here : [https://github.com/WafaJohal/RAnalysis_Thymio_AR_Optique.git]

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(plotly)
library(plyr)
library(ggplot2)
library("ggthemes")
library("scales")
#library(RQDA)

library(png)
library(grid)
library(reshape2)
library(readr)
```
```{r, echo=FALSE, message=FALSE, include=FALSE}
AR_results <- read_csv("~/Documents/CODING/DATA_ANALYSIS/Thymio_AR/AR_results.csv", 
    col_types = cols(condition = col_factor(levels = c("WO_AR", "AR")), date = col_datetime(format = "%d/%m/%y"), teacher = col_factor(levels = c("FM","OR"))))
source("util.R")
attach(AR_results)
```

##Are the group balanced?
```{r, echo=FALSE, message=FALSE, warning=FALSE}
summ_freq = summarySE(AR_results, measurevar="average_grade", groupvars=c("group_id","condition"))
summ_freq[is.na(summ_freq)] <- 0
p = ggplot(summ_freq, aes(x=group_id, y=average_grade, fill=condition, group=1)) +
    geom_errorbar(aes(ymin=average_grade-sd, ymax=average_grade+sd), width=.1) +
    geom_bar(stat="identity") +theme_Publication()+  scale_fill_activities_Publication() 
ggplotly(p)
```



### Evolution of scores for each concept and for the two conditions
In average across all the sessions
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(plyr)
AR_results <- melt(AR_results, measure.vars=c("C11","C12","C13", "C21","C22","C23","C31","C32","C33","C41","C42","C43"))
names(AR_results)[names(AR_results)=="variable"] <- "Concept"
names(AR_results)[names(AR_results)=="value"] <- "C_Score"



tmp_s1 = subset.data.frame(AR_results, (AR_results$Concept == "C11" | AR_results$Concept =="C21" |
              AR_results$Concept == "C41" | AR_results$Concept == "C31"))
tmp_s1$Session = "1"
tmp_s2 = subset.data.frame(AR_results, (AR_results$Concept == "C12" | AR_results$Concept =="C22" |
              AR_results$Concept == "C42" | AR_results$Concept == "C32"))
tmp_s2$Session = "2"
tmp_s3 = subset.data.frame(AR_results, (AR_results$Concept == "C13" | AR_results$Concept =="C23" |
              AR_results$Concept == "C43" | AR_results$Concept == "C33"))
tmp_s3$Session = "3"

AR_results =  rbind(tmp_s1, rbind(tmp_s2,tmp_s3))

tmp_c1 = subset.data.frame(AR_results, (AR_results$Concept == "C12" | AR_results$Concept =="C11" | AR_results$Concept == "C13"))
tmp_c1$concept_id = "C1"
tmp_c2 = subset.data.frame(AR_results, (AR_results$Concept == "C22" | AR_results$Concept =="C21" | AR_results$Concept == "C23"))
tmp_c2$concept_id = "C2"
tmp_c3 = subset.data.frame(AR_results, (AR_results$Concept == "C32" | AR_results$Concept =="C31" | AR_results$Concept == "C33"))
tmp_c3$concept_id = "C3"
tmp_c4 = subset.data.frame(AR_results, (AR_results$Concept == "C42" | AR_results$Concept =="C41" | AR_results$Concept == "C43"))
tmp_c4$concept_id = "C4"

AR_results =  rbind(tmp_c1, rbind(tmp_c2,rbind(tmp_c3,tmp_c4)))

summ_freq = summarySE(AR_results, measurevar="C_Score", groupvars=c("concept_id","condition"))
summ_freq[is.na(summ_freq)] <- 0
attach(summ_freq)
p = ggplot(summ_freq, aes(x=condition, y=C_Score, fill=condition, group = factor(condition))) +
    geom_errorbar(aes(ymin=C_Score-sd, ymax=C_Score+sd), width=.1) +
    geom_bar(stat="identity",position = position_dodge(width = 0.9)) +theme_Publication() + facet_wrap(~concept_id)+ylim(0,1)+
   scale_fill_activities_Publication() 
ggplotly(p)
print(summ_freq)
```
For each session
```{r, echo=FALSE, message=FALSE, warning=FALSE}
summ_freq = summarySE(AR_results, measurevar="C_Score", groupvars=c("concept_id","condition","Session"))
summ_freq[is.na(summ_freq)] <- 0
attach(summ_freq)
p = ggplot(summ_freq, aes(x=Session, y=C_Score, fill=condition, group = factor(condition))) +
    geom_errorbar(aes(ymin=C_Score-sd, ymax=C_Score+sd), width=.1) +
    geom_bar(stat="identity",position = position_dodge(width = 0.9)) +theme_Publication() + facet_wrap(~concept_id)+ylim(0,1)+
   scale_fill_activities_Publication() 
ggplotly(p)
print(summ_freq)
attach(AR_results)
```


## Statistical test of significance
Is AR significantly different than WO_AR for the concept considered?
```{r}

summary(aov(C_Score ~ condition))
summary(aov(C_Score ~ Session))
summary(aov(C_Score ~ concept_id))
summary(aov(C_Score ~ group_id))
summary(aov(C_Score ~ condition*Session*concept_id))
```


